Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-02-01 ForegroundSimulations/ms.tex

Fig.~\ref{fig:asm-dps-beam-chromaticity} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern. In all these panels, power spectra obtained with achromatic, {\it Airy} disk and simulated disk are shown in black, red, and blue respectively. The vertical gray lines denote the horizon limits for a 14.6~m antenna spacing. The full band delay power spectra of the foregrounds measured on a 14.6~m antenna spacing oriented eastward is shown in the top left panel. A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity. For instance, the spillover from foreground delay power spectrum obtained with simulated dish pattern extends out to $k_\parallel \approx \pm 0.14\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it extends out to $k_\parallel \approx \pm 0.08\,h$~Mpc$^{-1}$, while the achromatic beam extends it only out to $k_\parallel \approx \pm 0.05\,h$~Mpc$^{-1}$. Thus an increase in chromaticity extends the foreground spillover into higher $k_\parallel$-modes making them inaccessible for EoR H{\sc i} signal detection.

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{asm_beam_chromaticity_subband_150_MHz.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra. }
\label{fig:asm-dps-beam-chromaticity}
\end{figure*}

>>>>

Fig.~\ref{fig:asm-dps-beam-chromaticity-14.6m-baseline} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern. In all these panels, power spectra obtained with achromatic, {\it Airy} disk and simulated disk are shown in black, red, and blue respectively. The vertical gray lines denote the horizon limits for a 14.6~m antenna spacing. The full band delay power spectra of the foregrounds measured on a 14.6~m antenna spacing oriented eastward is shown in the top left panel. A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity. For instance, the spillover from foreground delay power spectrum obtained with simulated dish pattern extends out to $k_\parallel \approx \pm 0.14\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it extends out to $k_\parallel \approx \pm 0.08\,h$~Mpc$^{-1}$, while the achromatic beam extends it only out to $k_\parallel \approx \pm 0.05\,h$~Mpc$^{-1}$. Thus an increase in chromaticity extends the foreground spillover into higher $k_\parallel$-modes making them inaccessible for EoR H{\sc i} signal detection.

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{asm_beam_chromaticity_bl2_LST_3.96_hrs_subband_150.0_MHz.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for a 14.6~m baseline.}
\label{fig:asm-dps-beam-chromaticity-14.6m-baseline}
\end{figure*}

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{asm_beam_chromaticity_bl8_LST_3.96_hrs_subband_150.0_MHz.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for a 29.2~m baseline.}
\label{fig:asm-dps-beam-chromaticity-29.2m-baseline}
\end{figure*}
